### 2021-02-27 math/ia_2021/paper.tex
ia work

\subsection{Processing the dataset for use}
%TODO: #2 Ask for help 
The dataset, procured from the NOAA website \cite{noaa}, includes many tsunami
runups, going back before the year 0. Due to this, the NOAA states uncertainties
that can occur in its data. For example, reports that were recorded before the
20th century tend to be based on written accounts, and not recorded seismic activity.
Only since the 1960s, the installation of the Worldwide Standardized Seismograph
Network system allowed for more accurate data in this paper. For that reason, any recorded
activity before this date was discarded from the dataset for this paper. The dataset itself can
be accessed through two different methods; searching the database using the online
tool or downloading it in a somewhat obscure compressed Google Earth \verb|.kmz| format. 
The online tool supports the download of search results in a much more human-readable 
\verb|.csv| format. For this paper, all entries after the year 1900 were searched and downloaded.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\textwidth]{modelshowcase.jpeg}
    \label{fig:boat1}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \subfloat[\centering Linear model]{{\includegraphics[width=5cm]{linear.png} }}
    \qquad
    \subfloat[\centering Polynomial model]{{\includegraphics[width=5cm]{poly.png} }}
    \caption{2 multivariate (hence the 3 dimensions) regression models}
    \label{fig:example}
\end{figure}

>>>>

\subsection{Processing the dataset for use}
%TODO: #2 Ask for help 
The dataset, procured from the NOAA website \cite{noaa}, includes many tsunami
runups, going back before the year 0. Due to this, the NOAA states uncertainties
that can occur in its data. For example, reports that were recorded before the
20th century tend to be based on written accounts, and not recorded seismic activity.
Only since the 1960s, the installation of the Worldwide Standardized Seismograph
Network system allowed for more accurate data in this paper. For that reason, any recorded
activity before this date was discarded from the dataset for this paper. The dataset itself can
be accessed through two different methods; searching the database using the online
tool or downloading it in a somewhat obscure compressed Google Earth \verb|.kmz| format. 
The online tool supports the download of search results in a much more human-readable 
\verb|.tsv| (tab-separated) format. For this paper, all entries after the year 1900 were searched and downloaded.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{modelshowcase.jpeg}
    \label{fig:boat1}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \subfloat[\centering Linear model]{{\includegraphics[width=7.5cm]{linear.png} }}
    \qquad
    \subfloat[\centering Polynomial model]{{\includegraphics[width=7.5cm]{poly.png} }}
    \caption{2 multivariate (hence the 3 dimensions) regression models}
    \label{fig:example}
\end{figure}
